---
title: "temp2"
output: html_document
date: "2023-02-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
data<-read.table("C:/Users/HP/Downloads/DataMaster_v1.csv",header = TRUE,sep=',')
attach(data)
train=data[1:1000,]
test=data[1001:1235,]

plot.ts(train$TATA_close)
acf(train$TATA_close,lag=50)
Box.test(train$TATA_close, type="Ljung", lag=50)

plot.ts(diff(train$TATA_close))
acf(diff(train$TATA_close),lag=50)
Box.test(diff(train$TATA_close), type="Ljung", lag=20)

```


$\bullet$Visually, there exists an autocorrelation issue (the residuals are not white noise). 

$\bullet$
$H_0:All\ autocorrelations\ are\ 0\ vs\ H_a:at\ least\ one\ autocorrelation\ is\ different\ than\ 0$ 

The formal test indicates that the residuals are autocorrelated. Since the p-value (â‰ˆ 0) is less than ð›¼ (0.05), we reject the null hypothesis. The residuals are autocorrelated.


```{r}
newdata=train[-c(1)]
pairs(newdata,lower.panel = NULL)
cor(newdata)

mlr<-lm(TATA_close~.,data = newdata)
summary(mlr)

#Auto-correlation test
sres<-rstandard(mlr)
acf(sres, lag=30)
acf(sres, plot=FALSE)
Box.test(sres,type = "Ljung", lag=20)
```


```{r}
#Normality test
library(nortest)
shapiro.test(sres)
hist(sres,breaks=15, col="steelblue")

```


$\bullet$
$H_0:Series\ are\ normally\ distributed\ vs\ H_a:Series\ are\ not\ normally\ distributed$  
The formal test indicates that residuals are not normally distributed. Since the p-value(â‰ˆ 0) is less than ð›¼ (0.05) we reject the null hypothesis. 

```{r}
#Hetroskedasity test
#install.packages("skedastic")
library(skedastic)
white(mlr,interactions = TRUE)

```


$\bullet$ 
$H_0:There\ is\ no\ Heteroscedasticity(constant\ variance)\ vs\\ H_a:There\ is\ Heteroscedasticity(non-constant\ variance)$ 

The formal test indicates that the residuals exhibit non-constant variance.
Since the p-value (â‰ˆ 0) is less than ð›¼ (0.05), we reject the null hypothesis. The
residuals are heteroscedastic. 


```{r}
#Deterministic time series model
#hours=rep(c(1:24),times=412)[1:9886]
time=seq(1:length(diff(train$TATA_close)))
fit<-lm(diff(TATA_close)~time,data=train)
summary(fit)
sres=rstandard(fit)
acf(sres)
Box.test(sres,type = "Ljung", lag=20)
#Residuals are not white noise

```


```{r}
#Polynomial model
k=8
fit1<-lm(diff(TATA_close)~poly(time,k),data=train)
summary(fit1)

k=1
fit1<-lm(diff(TATA_close)~poly(time,k),data=train)
summary(fit1)

sres=rstandard(fit1)
acf(sres)
Box.test(sres,type = "Ljung", lag=20)

```


```{r}
library(TSA)
fit2<-lm(diff(TATA_close)~time,data=train)
periodogram(fit2$residuals)
periodogram(fit2$residuals)$spec
order(periodogram(fit2$residuals)$spec,decreasing = TRUE)

n<-length(diff(train$TATA_close))

acf(diff(TATA_close))
pacf(diff(TATA_close))

fit4=arima(train$TATA_close,order = c(2,1,2))
acf(fit4$residuals)

sarima.fit <- arima(train$TATA_close, order = c(1, 1, 1), seasonal=list(order=c(1,1,0), period=4))
(sarima.fit)
acf(sarima.fit$residuals)


library(fGarch)
garch.fit<-garchFit(~garch(1,1),data=diff(train$TATA_close), trace=FALSE)
summary(garch.fit)
acf(garch.fit@residuals/garch.fit@sigma.t, main="Residuals",lag=50)
Box.test(garch.fit@residuals/garch.fit@sigma.t, lag=100)

acf((garch.fit@residuals/garch.fit@sigma.t)^2, main="Squared Residuals")
```